---
title: "Alcohol vs Seat choice"
author: "Tiffany Alvarado"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??


## Method
predict alcohol consumption based on where you sit  

$H_0$ No diff in alcohol cons based on where you sit  
$H_A$ There is a difference based on where you sit  

alcohol is numerical  
seat is catagorical so we use the helper file num~cat  


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The boxplot shows that the drunks sit mostly in the back. 
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The average for people in the back is higher (3.5) then the people in the middle which is (1.0) and even higher then the people sitting in the front (0)
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```

## Conclusions
In conclusion the tukey is saying that our P-value is 0.000116 which is lower than .05 so we reject the null hypthosis. The data we were trying to find is if there is no difference in where you sit which is wrong because the mean shown on the tukey is 0. 
